% !TEX program = xelatex

\documentclass{resume}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Tianchen Zhong}

\basicInfo{
  \email{tzhong1@andrew.cmu.edu} 
  \phone{412-616-3343} 
  \linkedin[tianchen-zhong]{https://www.linkedin.com/in/tianchen-zhong}
  \github[cczhong11]{https://github.com/cczhong11}
  \homepage[tczhong.com]{http://www.tczhong.com}
}

\section{Education}
\datedsubsection{\textbf{Carnegie Mellon University (CMU)}}{Pittsburgh, PA} 
\role{Master of Science in Information Networking; GPA: 3.95/4.0} {\hfill Aug. 2017 - May 2019}
\begin{itemize}
\item{\textbf{Related Courses}: Intro to Computer Systems, Cloud Computing, Search Engine, Distributed System, Artificial Intelligence, Practical Data Science}
\end{itemize}
\datedsubsection{\textbf{Southeast University (SEU)}}{Nanjing, China} 
\role{Bachelor of Engineering in Information Engineering; GPA: 3.89/4.0 (91.64/100)} {\hfill Aug. 2013 - June 2017}
\begin{itemize}
\item{\textbf{Related Courses}: Data Structures and Algorithm, Database System, Machine Learning,  Computer Architecture, BigData, Computer Vision, Computer Network}
\end{itemize}

\section{Skills}
\begin{itemize}
\item \textbf{Programming Language}: {Java, Python, C, JavaScript, SQL, Golang, Scala}
\item \textbf{Cloud}: {AWS: EC2, S3, Lambda, DynamoDB, RDS, EMR, Azure: CosmosDB, Functions, App service,Blob Storage, Event Hubs, GCP: Dataproc, Compute Engine, Kubernetes Engine, Datastore, Functions}
\item \textbf{DataBase and Big Data}: {MySQL, HBase, MongoDB, CosmosDB, Spark, Hadoop MapReduce, Kafka}
\end{itemize}


\section{Internship}
\datedsubsection{\textbf{Walmart Inc}}{Bentonville, AR} 
\role{Software Engineer Intern in Sam's Club Cloud infrastructure team} {\hfill   May - Aug. 2018}
\begin{itemize}
\item{Developed \textbf{Azure} \textbf{CosmosDB} resource auto scaling system both backend and frontend with \textbf{Java Spring} Framework and \textbf{ReactJS}, reducing 70\% cost by only using high capacity in scheduled time.}
\item{Designed and Implemented \textbf{RESTful API} and highly scalable backend that can manage autoscaling of 1000's of \textbf{CosmosDB} instances with \textbf{Azure} \textbf{Web App}, \textbf{CosmosDB}, \textbf{Functions}, \textbf{Event Hubs}.}
\item{Won third prize in Walmart Codeception Hackathon with implementing Java backend for a location focused social media platform for Walmart associates.}
\end{itemize}
\datedsubsection{\textbf{Intel Asia-Pacific Research \& Development Ltd.}}{Shanghai, China} 
\role{Software Development and Validation Intern} {\hfill   July - Dec. 2016}
\begin{itemize}
\item{Developed and upgraded test scripts and architectures for LPSS(Low Power Sub-System) testing code.}
\item{Built \textbf{Python} automation tool to accelerate average testing time by 20\%.}
\item{Collaborated with security team to develop a demo for proof of concept of secure container with \textbf{Node.js}, \textbf{HTML5} and \textbf{Docker} and helped team win the customer.}
\end{itemize}

\section{Projects}
\datedsubsection{\textbf{Twitter Analytics Web Service}}{Feb. - May 2018} 
\begin{itemize}
\item{Performed data Extracted, Transform and Load on 300 million (1TB) of raw tweet messages using \textbf{Spark}.}
\item{Built a RESTful web service using Undertow framework, with \textbf{MySQL} and HBase as back-end on \textbf{AWS}.}
\item{Applied load balancing strategy to handle 4 types of intensive read/write queries and achieved an average of 10,000 QPS (queries per second) in 2 hours live test, within a maximum cost of \$0.85/h on \textbf{AWS}.}
\item{Optimized web service by using thread pool, refining database schema, tuning parameters on backend database. Utilized \textbf{JMeter} as load generator to test our web service.}
\end{itemize}
\datedsubsection{\textbf{Lucene Based Search Engine}}{Jan. - May 2018} 
\begin{itemize}
\item{Implemented a text-based search engine indexed with Lucene API on corpus of 500, 000 + documents from ClueWeb09 dataset in \textbf{Java}.}
\item{Developed a custom search engine with diversification, query expansion and learning to rank capability, supporting retrieval models including Ranked Boolean, BM25, and language statistic model like Indri.}
\item{Evaluated the models developed by varying parameter values, analyzed trends, ambiguities discovered from the conducted experiments.}
\end{itemize}
\datedsubsection{\textbf{Introduction to Computer system}}{Sept. - Dec. 2017} 
\begin{itemize}
\item{Developed dynamic storage allocator in \textbf{C} using explicit, segregated lists and improved space utilization by reduce header in the allocator block.}
\item{Designed a \textbf{web proxy} supporting HTTP/1.0 requests and implemented multi-thread to deal with multiple concurrent connections and added LRU cache to reduce the response time.}
\end{itemize}

\end{document}
